---
title: "Assignment 3 Markdown"
authors: Marygrace, Edwison, Gyasi
date: March 31st, 2018
output: html_document
---

This is the R markdown for Assignment 3 BIO439.
Marygrace has master repository with Edwison and Gyasi as forked collaborators
We will be constructing 3 plots representing 3 different reflationships from the data given.


The first will display the Hindfoot Length of Male vs. Female for Dipodomys merriami.


Let's first load the libraries
```{r results='hide', message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
```


And install respective packages making sure to include the cloning path to the GitHub repository
```{r cache=FALSE, results=FALSE, warning=FALSE, comment=FALSE}
install.packages("dplyr", repos = "https://github.com/mtrousdell/Assignment3_BIO439.git")
install.packages("tidyverse", repos = "https://github.com/mtrousdell/Assignment3_BIO439.git")
```


Now, read in the data and assign to its respective variable for ease of reference.
```{r results='hide', message=FALSE, warning=FALSE}
combined_data <- read_csv('combined.csv')
plots_data <- read_csv('plots.csv')
species_data <- read_csv('species.csv')
surveys_data <- read_csv('surveys.csv')
```


Isolate from the imported data the 3 variables of interest (sex, species_id, hindfootlength) and assign to a variable. Remove any NA's existing.
```{r results='hide', message=FALSE, warning=FALSE}
Three_variables <- surveys_data[,6:8] %>% filter(!is.na(hindfoot_length)) %>% filter(!is.na(sex)) 
```



Isolate only the data for Dipodomys merriami.
```{r results='hide', message=FALSE, warning=FALSE}
DM_data <- filter(Three_variables, species_id == 'DM')
```


You can use the simple summary command to get quick stats on your data, just to have an idea of what to expect.
```{r results='hide', message=FALSE, warning=FALSE}
summary(DM_data)
```



Now that we know some specifics of the data we are dealing with, we shall plot using ggplot.
First install the library and package.
```{r results='hide', message=FALSE, warning=FALSE}
install.packages("ggplot2", repos = "https://github.com/mtrousdell/Assignment3_BIO439.git")
library(ggplot2) 
```


Start off with the simple aesthetics of a boxplot and assign to a simple variable.
```{r results='hide', message=FALSE, warning=FALSE}
p <- ggplot(data = DM_data, aes(x = sex, y = hindfoot_length)) + geom_boxplot()
```


Add to that variable and spice it up with axis labels and summary data.
```{r results='hide', message=FALSE, warning=FALSE}
q <- p + ggtitle("Species 'DM' Male vs. Female Hindfoot Lengths") +
  xlab("Sex") + ylab("Hindfoot Lengths")
q + stat_summary(fun.y=mean, geom="point", color="blue", size=4) + 
  geom_jitter(shape=16, position=position_jitter(0.2), alpha = .010)

```









