---
title: "Assignment 3 Markdown"
authors: Marygrace, Edwison, Gyasi
date: March 31st, 2018
output: html_document
---

This is the R markdown for Assignment 3 BIO439.
We will be constructing 3 plots representing 3 different relationships from the data given.



The first will display the Hindfoot Length of Male vs. Female for Dipodomys merriami.



Install packages making sure to include the cloning path to the GitHub repository.
```{r cache=FALSE, results=FALSE, warning=FALSE, comment=FALSE}
install.packages("dplyr", repos = "https://github.com/mtrousdell/Assignment3_BIO439.git")
install.packages("tidyverse", repos = "https://github.com/mtrousdell/Assignment3_BIO439.git")
install.packages("ggpubr", repos = "https://github.com/mtrousdell/Assignment3_BIO439.git")
install.packages("ggplot2", repos = "https://github.com/mtrousdell/Assignment3_BIO439.git")
```




Then load the respective libraries
```{r results='hide', message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(ggpubr)
library(ggplot2)
```




Now, read in the data and assign to its respective variable for ease of reference.
```{r results='hide', message=FALSE, warning=FALSE}
combined_data <- read_csv('combined.csv')
plots_data <- read_csv('plots.csv')
species_data <- read_csv('species.csv')
surveys_data <- read_csv('surveys.csv')
```




Isolate from the imported data the 3 variables of interest (sex, species_id, hindfootlength) and assign to a variable. Remove any NA's existing.
```{r results='hide', message=FALSE, warning=FALSE}
Three_variables <- surveys_data[,6:8] %>% filter(!is.na(hindfoot_length)) %>% filter(!is.na(sex)) 
```




Isolate only the data for Dipodomys merriami.
```{r results='hide', message=FALSE, warning=FALSE}
DM_data <- filter(Three_variables, species_id == 'DM')
```




Now we will plot using ggplot.
Start off with the simple aesthetics of a boxplot and assign to a simple variable.
```{r results='hide', message=FALSE, warning=FALSE}
p <- ggplot(data = DM_data, aes(x = sex, y = hindfoot_length)) + geom_boxplot()
```




Add to that variable and spice it up with axis labels and summary data.
```{r results='hide', message=FALSE, warning=FALSE}
q <- p + ggtitle("Species 'DM' Male vs. Female Hindfoot Lengths") +
  xlab("Sex") + ylab("Hindfoot Lengths")
q + stat_summary(fun.y=mean, geom="point", color="blue", size=4) + 
  geom_jitter(shape=16, position=position_jitter(0.2), alpha = .010)

```





For the second and third plot we want to plot the relationship between Hindfoot Length vs. Weight for Male and Female for Dipodomys merriami.




We will use similar code structure from the first plot. First, we isolate from the imported data the 4 variables of interest (sex, species_id, hindfootlength, weight) and assign to a variable, making sure to rid of any NA's.
```{r results='hide', message=FALSE, warning=FALSE}
Four_variables <- surveys_data[,6:9] %>% filter(!is.na(hindfoot_length)) %>% filter(!is.na(sex)) %>%
  filter(!is.na(weight))
```




Subset this data down to just species Dipodomys merriami
```{r results='hide', message=FALSE, warning=FALSE}
DM_data2 <- filter(Four_variables, species_id == 'DM')
```




Further subset the data according to gender and assign to a variable
```{r results='hide', message=FALSE, warning=FALSE}
DM_male <- filter(DM_data2, sex == 'M')
DM_female <- filter(DM_data2, sex == 'F')
```




Create the plot for Male
```{r results='hide', message=FALSE, warning=FALSE}
ggscatter(DM_male, x = "hindfoot_length", y = "weight",title = "Relationship between weight and hindfoot_length of Male DM", xlab = "Hindfoot_length(mm)", ylab = "weight(gm)",
          add = "reg.line",  # Add regression line
          add.params = list(color = "blue", fill = "lightgray"), # Customize reg. line
          conf.int = TRUE ) + stat_cor(method = "pearson", label.x = 20, label.y = 200)
```




and plot for Female
```{r results='hide', message=FALSE, warning=FALSE}
ggscatter(DM_female, x = "hindfoot_length", y = "weight",title = "Relationship between weight and hindfoot_length of Male DM", xlab = "Hindfoot_length(mm)", ylab = "weight(gm)",
          add = "reg.line",  # Add regressin line
          add.params = list(color = "blue", fill = "lightgray"), # Customize reg. line
          conf.int = TRUE ) + stat_cor(method = "pearson", label.x = 20, label.y = 200)
```





















