---
title: "Assignment 3 Markdown"
authors: Marygrace, Edwison, Gyasi
date: March 31st, 2018
output: html_document
---

This is the R markdown for Assignment 3 BIO439.
We will be constructing 3 plots representing 3 different relationships from the data given.



The first will display the Hindfoot Length of Male vs. Female for Dipodomys merriami.



Install packages making sure to include the cloning path to the GitHub repository.
```{r cache=FALSE, results=FALSE, warning=FALSE, comment=FALSE}
install.packages("dplyr", repos = "https://github.com/mtrousdell/Assignment3_BIO439.git")
install.packages("tidyverse", repos = "https://github.com/mtrousdell/Assignment3_BIO439.git")
install.packages("ggpubr", repos = "https://github.com/mtrousdell/Assignment3_BIO439.git")
install.packages("ggplot2", repos = "https://github.com/mtrousdell/Assignment3_BIO439.git")
```




Then load the respective libraries
```{r results='hide', message=FALSE, warning=FALSE}
library(readr)
library(dplyr)
library(ggpubr)
library(ggplot2)
```




Now, read in the data and assign to its respective variable for ease of reference.
```{r results='hide', message=FALSE, warning=FALSE}
combined_data <- read_csv('combined.csv')
plots_data <- read_csv('plots.csv')
species_data <- read_csv('species.csv')
surveys_data <- read_csv('surveys.csv')
```

















